Parallel Information Set Generation for Kriegspiel

### 2012-07-16 sbac/paper.tex
more conclusion

However, in the game of Kriegspiel, information set generation is much more complicated.
After the first move by the opponent, a player faces uncertainty about the
location of the opponent's pieces.  Unlike Poker, it is not possible to simply
permute all of the opponent's possible pieces over all of the squares not
occupied by the player's own pieces.  A configuration of pieces for the
opponent is only valid if it can be reached by a legal sequence of moves.  In
the general case, finding the nodes in an information set is a combinatorial
search problem.

In this work, we show that ISG for Kriegspiel can be efficiently parallelized.
The primary contributions of this work are the following:
\begin{itemize}
\item
 We describe an
approach to efficient parallelization of an application which is not typical of
high performance computing and scientific domain, yet important because of its usefulness in the field of artificial intelligence.
\item
 We present scalability results for our
parallel implementation of an information set generation algorithm for the game
of Kriegspiel using problem instances from real games. We achieve results which are unprecedented in game tree search application. 
\item
We demonstrate
the effects of load balancing strategy and grainsize on the parallel performance of our implementation. 
\end{itemize}

@@

\section{Kriegspiel}\label{Kriegspiel}
Information Set Generation is the process of identifying the nodes in an
imperfect information game tree that are consistent with a player's
observations~\cite{richards12information}. Here, we present our techniques and
results in the context of a particular game: Kriegspiel~\cite{li94chess}.
However, the techniques and framework presented in this paper are general and
can be applied to ISG in other imperfect information games.

@@

\section{Conclusion and Future Work}
We have shown that information set generation for Kriegspiel can be efficiently
parallelized.  The opportunities for parallelism increase as the problem size
increases.  Our algorithm has performed well on problems with information sets
with as many as 65 million nodes --- much larger than any other treatment of the
problem that we are aware of.

>>>>

However, for many games (such as Kriegspiel), information set generation is much more complicated.
After the first move by the opponent, a player faces uncertainty about the
location of the opponent's pieces.  Unlike Poker, it is not possible to simply
permute all of the opponent's possible pieces over all of the squares not
occupied by the player's own pieces.  A configuration of pieces for the
opponent is only valid if it can be reached by a legal sequence of moves.  In
the general case, finding the nodes in an information set is a combinatorial
search problem.

In this work, we show that ISG for Kriegspiel can be efficiently parallelized.
The primary contributions of this work are the following:
\begin{itemize}
\item
 We describe an
approach to efficient parallelization of an application - information set generation,  which is not typical of
high performance computing and scientific domain, yet important because of its usefulness in the field of artificial intelligence.
\item
 We present scalability results for our
parallel implementation of an information set generation algorithm for the game
of Kriegspiel using problem instances from real games. We achieve results which are unprecedented in game tree search application. 
\item
We demonstrate
the effects of load balancing strategy and grainsize on the parallel performance of our implementation. 
\end{itemize}

@@

\section{Background}\label{Kriegspiel}
Information Set Generation is the process of identifying the nodes in an
imperfect information game tree that are consistent with a player's
observations~\cite{richards12information}. Here, we present our techniques and
results in the context of a particular game: Kriegspiel~\cite{li94chess}.
However, the techniques and framework presented in this paper are general and
can be applied to ISG in other imperfect information games.
%\subsection{Kriegspiel}

@@

\section{Conclusion and Future Work}
In this paper, we showed that information set generation for Kriegspiel can be efficiently
parallelized.  Through extensive experimentation, we demonstrated that the choice of a suitable load balancing strategy and optimal grain size control is crucial to achieve good scalability for parallel ISG. The opportunities for parallelism increase as the problem size
increases.  Our algorithm has performed well on problems with information sets
with as many as 65 million nodes --- much larger than any other treatment of the
problem that we are aware of.
